\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-29 lang-design.tex
Reply comments first so that yizhou can continue to read
Save. Rewriting

>>>>

\subsection{Challenges}

We want our metatheory mechanization to allow adding new function/proving new lemmas (Expression Problem), and adding new constructors for inductive type at the same time. Coq support the former but not the later---because when an existent inductive type is extended with new constructor, we have to modify the pattern matching in the existent functions. This motivates us to add inheritance/Family Polymorphism into Coq.

However, to add inheritance into a dependent type system like Coq is not simple and there are some challenges we need to resolve.
